Luminosity function and flux function\\ or\\ How far to the brightest beacon?

### 2015-12-14 luminosity.tex
Switch order of n_r equation
didn't I push the revision I made last time...?

\begin{abstract}
%We examine how the highest observed flux evolves as we observe further. 
%This question is motivated because it appears to be a competition between the fact that the observed flux decreases as the objects are located further, and the fact that the number of targets increases as we observe further. 
Within a sphere centered on an observer, is the apparently-brightest source likely to be near the center of the sphere or near the periphery?
The answer is not obvious because near the center (near the observer), brightness is increased by the inverse square law; however, far from the observer, there is much more volume available.
%
To answer this question, we calculate the expected value of the highest flux from a given spherical shell and see whether the expected value increases as a function of distance (radius) of the sphere. 
In doing so, we consider  a luminosity function characterized by a power law with lower and upper limits of luminosity.
We find the expected value of the highest flux monotonically decreases as a function of radius of the spherical shell, and thus we are not likely to find the brightest object far away.
%we calculate the expected value of the highest flux from a given spherical shell and see whether the expected value increases as a function of distance (radius) of the sphere. 
%firstly we consider the distribution of observed flux from a sphere within distance $R$ of a given luminosity function ("flux function"). The flux function composes of three regimes: in order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5. 
%Then, we compute the expected value of the highest flux from a spherical shell at distance $R\sim R+dR$. within a volume with radius $R$. 
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{Prob_alpha15.pdf}
   \plotoneh{Prob_alpha31.pdf}
   \caption{Flux distribution of sources in a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
  \label{fig:prob}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Let us consider the distribution of fluxes from sources from a spherical shell at distance $r$ with thickness $dr$.
The ({\it expected}) total number of the sources within that spherical shell is
%%%
\begin{equation}
4 \pi r^2 dr \int _0 ^{\infty} \frac{d^2 N}{dF~dr} dF \equiv n_r. 
\end{equation}
%%%
\memoYF{not sure how to deal with the fact that this is expected number.}

The probability that a source within the spherical shell has a flux between $F\sim F+dF$, $P[F]dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
%%%
\begin{equation}
P[F] dF = C' F^{\alpha } r^{4-2\alpha }
\end{equation}
%%%
where
%%%
\begin{equation}
C' = n_r \left( \int _0 ^{\infty}P[F]~dF~\right)^{-1}
\end{equation}
%%%

The probability that the maximum flux lies in the range between $F_{\rm max}$ and $F_{\rm max} + dF_{\rm max}$, denoted $\mathcal{P} [F_{\rm max}] dF_{\rm max}$, is the joint probability that one of the targets has flux between $F_{\rm max}$ and $F_{\rm max} + dF_{\rm max}$ and that all others have smaller flux.
The probability that one object has flux lower than $F'$ is
%%%
\begin{equation}
P [<F'] = \int _{-\infty} ^{F'}  P [F] \; dF 
\end{equation}
%%%
Noting that we have $n_r$ ways to select the target with the highest flux, such a probability is:
%%%
\begin{equation}
\mathcal{P} [F_{\rm max}] dF_{\rm max} = n_r P [< F_{\rm max}]^{n_r-1}  P[F_{\rm max}] dF_{\rm max} %\\
%&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
%&\sim & N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - ( N_R -1 ) P (> F_{\rm max}) \right]
\end{equation}
%%%

The expected value of the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm max} \rangle$, is obtained by calculating the flowing integral. 
%%%
\begin{eqnarray}
\langle F_{\rm max} \rangle &=& \int dF_{\rm max} \, F_{\rm max} \mathcal{P} [F_{\rm max}] \\
&=& n_r \int dF_{\rm max} F_{\rm max} P [< F_{\rm max}]^{n_r-1}  P[F_{\rm max}]
\end{eqnarray}
%%%

Figure \ref{fig:expectedFmax} shows $\langle F_{\rm max} \rangle$ as a function of distance $r$ with varying number density of the sources. 
Again, examples for $\alpha = 3.1$ and $\alpha = 1.5$, with $L_{\rm min } = 7.0\times 10^3 ~{\rm W/Hz}$ and $L_{\rm max} = 1.5\times 10^{13} ~{\rm W/Hz}$ are shown. 
It is seen that the expected values monotonically decrease as we observe further. This indicates the brightest object is the closest one. \memoYF{??}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{expectedFmax_alpha31.pdf}
   \plotoneh{expectedFmax_alpha15.pdf}
   \caption{Expected value for the maximum flux in $\mu {\rm Jy}$ from a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
  \label{fig:expectedFmax}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{abstract}
%We examine how the highest observed flux evolves as we observe further. 
%This question is motivated because it appears to be a competition between the fact that the observed flux decreases as the objects are located further, and the fact that the number of targets increases as we observe further. 
Within a sphere centered on an observer, is the apparently-brightest source likely to be near the center of the sphere or near the periphery?
The answer is not obvious because near the center (near the observer), brightness is increased by the inverse square law; however, far from the observer, there is much more volume available.
%
To answer this question, we calculate the expected value of the highest flux from a given spherical shell and see whether the expected value increases as a function of distance (radius) of the sphere. 
In doing so, we consider  a luminosity function characterized by a power law with lower and upper limits of luminosity.
We find that \memoYF{...}
%the expected value of the highest flux monotonically decreases as a function of radius of the spherical shell, and thus we are not likely to find the brightest object far away. 
%we calculate the expected value of the highest flux from a given spherical shell and see whether the expected value increases as a function of distance (radius) of the sphere. 
%firstly we consider the distribution of observed flux from a sphere within distance $R$ of a given luminosity function ("flux function"). The flux function composes of three regimes: in order of increasing flux, 1) zero flux, 2) a power law which depends on the luminosity function, and 3) a power law with index -2.5. 
%Then, we compute the expected value of the highest flux from a spherical shell at distance $R\sim R+dR$. within a volume with radius $R$. 
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{Prob_alpha10.pdf}
   \plotoneh{Prob_alpha30.pdf}
   \caption{Flux distribution of sources in a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) .}
  \label{fig:prob}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Let us consider the distribution of fluxes from sources from a spherical shell at distance $r$ with thickness $dr$.
The ({\it expected}) total number of the sources within that spherical shell is
%%%
\begin{equation}
n_r \equiv dr \int _0 ^{\infty} \frac{d^2 N}{dF~dr} dF \, . 
\end{equation}
%%%
\memoYF{not sure how to deal with the fact that this is expected number.}

The probability that a source within the spherical shell has a flux between $F\sim F+dF$, $P[F]dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
%%%
\begin{equation}
P[F] dF = \left\{
\begin{array}{ll}
C' F^{\alpha } r^{4-2\alpha } dF & (F_{\rm min}(r) < F < F_{\rm max}(r)) \\
0 & (\mbox{elsewhere})
\end{array}
\right. 
\end{equation}
%%%
where
%%%
\begin{eqnarray}
C' &=& n_r \left( \int _0 ^{\infty}P[F]~dF~\right)^{-1} \\
F_{\rm min}(r) &=& L_{\rm max} / 4 \pi r^2 \\
F_{\rm max}(r) &=& L_{\rm max} / 4 \pi r^2
\end{eqnarray}
%%%

The probability that the bright flux lies in the range between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$, denoted $\mathcal{P} [F_{\rm bright}] dF_{\rm bright}$, is the joint probability that one of the targets has flux between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$ and that all others have smaller flux.
The probability that one object has flux lower than $F'$ is
%%%
\begin{equation}
P [<F'] = \int _{-\infty} ^{F'}  P [F] \; dF 
\end{equation}
%%%
Noting that we have $n_r$ ways to select the target with the highest flux, this probability is:
%%%
\begin{equation}
\mathcal{P} [F_{\rm bright}] dF_{\rm bright} = n_r P [< F_{\rm bright}]^{n_r-1}  P[F_{\rm bright}] dF_{\rm bright} %\\
%&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
%&\sim & N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - ( N_R -1 ) P (> F_{\rm max}) \right]
\end{equation}
%%%

The expected value of the maximum flux among the targets within a spherical shell at radius $r$ (with width $dr$), $\langle F_{\rm bright} \rangle$, is obtained by calculating the flowing integral. 
%%%
\begin{eqnarray}
\langle F_{\rm bright} \rangle &=& \int dF_{\rm bright} \, F_{\rm bright} \mathcal{P} [F_{\rm bright}] \\
&=& n_r \int dF_{\rm bright} F_{\rm bright} P [< F_{\rm bright}]^{n_r-1}  P[F_{\rm bright}]
\end{eqnarray}
%%%

Figure \ref{fig:expectedFmax} shows $\langle F_{\rm bright} \rangle$ as a function of distance $r$ with varying number density of the sources. 
%It is seen that the expected values monotonically decrease as we observe further. This indicates the brightest object is the closest one. \memoYF{??}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htbp]
   \plotoneh{expectedvalues_alpha-1_Lmin-1_Lmax-1000000_Npc3-1e-3.pdf}
   \plotoneh{expectedvalues_alpha-15_Lmin-1_Lmax-1000000_Npc3-1e-3.pdf}
   \plotoneh{expectedvalues_alpha-3_Lmin-1_Lmax-1000000_Npc3-1e-3.pdf}
   \caption{Expected value for the maximum flux from a spherical shell at distance $r$ with unit width $\Delta r = 1{\rm pc}$ (arbitrary) in the case of the number density of the objects is $10^{-3}\,{\rm pc^{-3}}$. Blue and red dashed lines show $F_{\rm max} = L_{\rm max}/4\pi r^2$ and $F_{\rm min} = L_{\rm min}/4\pi r^2$, respectively. Something is wrong with $\alpha=1.0$ case at $3000<F$.}
  \label{fig:expectedFmax}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
